% NOT GRAMMA FIXED

\section{Conclusion and Research Question}

The report covered activities of the past semester. We created the application of simulation user actions. The Simulator is already used for generating login and logout events. But the project needs to be improved. Firstly it has a problem with stability. It means that in some case the program could determine the VM state incorrect that effect on the incorrect simulation. So the most important issue that must be solved. Secondly, we plan to move away from checking the VM state by screenshots, because it makes the program not stable in some cases. Thirdly, we plan to implement more complex scenarios of user actions. The program could be improved by extending types of user action and not to bound only by login and logout events. It give us possibility to write more complex scenarios. And for that reason we supposed to migrate the description of user scenarios from csv files to the database to make it more consistence and easier to use and add new scenarios.    

Regarding SLG project we plan to migrate the project into other OpenStack. It makes the project able to use for teaching and CTF seminars. It could be the first step towards Open Research Cloud. During implementation SLG based on OpenStack we try to ask on some research questions: 
\begin{compactitem}
\item How to decompose the project to make useful research tools?
\item How to specify the API for collaboration work?
\item How to share research results with other project based on OpenStack?
\item How to normalize research data to make them searchable, indexable and reusable?  
\end{compactitem}