\section{Introduction}

One of the most important factors of the progress in Computer Science is open-source projects. There is the following idea that if you write something interesting then please share with community. Also open-source projects include the idea that everyone can contribute thereby forces the progress. Open-source projects are firstly open and then free. Free is just a consequence of openness.

The scientific world has some problems that slow down the research progress. Most of them are obvious. One of them is the lack of data. Researchers need data for researches. The huge amount of data belong to industrial companies, but they do not hurry to share them because of security and privacy reasons. Researchers have to generate and simulate data. Further, many researchers need to configure the test network environment to perform research. It means that they have to run virtual machines (VMs), install applications, configure the network. Another problem is that during the research process, researchers usually create a lot of additional support tools. But the same tools can be created by other researchers. Tools can be open-source or not. Even if they are open-source it does not mean that you can easily use it in your particular case.  
 
To perform research is very important to have the necessary data, resources, the opportunity to work with colleagues from other areas. The academic world understands the importance of collaboration. As a result, many countries and universities are taking steps to make research more open and move research on the common environment. Thereby increasing of a productivity of scientists and accelerating a progress. There are several examples of creating some kind of Open Research clouds\footnote{Some of them will be mentioned in the section 4.1 Related Works.}.

