
%\input{mylib.bbl}
%\bibliographystyle{IEEEtran}
%%\bibliographystyle{ieeetr}
%\bibliography{mylib}

\begin{thebibliography}{10}
\providecommand{\url}[1]{#1}
\csname url@rmstyle\endcsname
\providecommand{\newblock}{\relax}
\providecommand{\bibinfo}[2]{#2}
\providecommand\BIBentrySTDinterwordspacing{\spaceskip=0pt\relax}
\providecommand\BIBentryALTinterwordstretchfactor{4}
\providecommand\BIBentryALTinterwordspacing{\spaceskip=\fontdimen2\font plus
\BIBentryALTinterwordstretchfactor\fontdimen3\font minus
  \fontdimen4\font\relax}
\providecommand\BIBforeignlanguage[2]{{%
\expandafter\ifx\csname l@#1\endcsname\relax
\typeout{** WARNING: IEEEtran.bst: No hyphenation pattern has been}%
\typeout{** loaded for the language `#1'. Using the pattern for}%
\typeout{** the default language instead.}%
\else
\language=\csname l@#1\endcsname
\fi
#2}}

\bibitem{OpenScienceDataCloud}
Open Science Data Cloud. https://www.opensciencedatacloud.org.

\bibitem{MOC}
Massachusetts Open Cloud. http://www.bu.edu/hic/projects/massachusetts-open-cloud/.

\bibitem{OpenCloudeXchange}
Open Cloud eXchange. http://www.cs.bu.edu/fac/best/res/papers/ic14.pdf.

\bibitem{NeCTAR}
National eResearch Collaboration Tools and Resources. http://nectar.org.au.

\bibitem{OpenStack}
OpenStack. http://www.openstack.org.

\bibitem{OpenNebula}
OpenNebula. http://opennebula.org.

\bibitem{Eucalyptus}
Eucalyptus. https://www.eucalyptus.com.

\bibitem{Cocaine}
Cocaine. http://api.yandex.com/cocaine.

\bibitem{CloudStack}
CloudStack. http://cloudstack.apache.org.

\bibitem{CloudComputingComparison}
Cloud computing comparison. http://drsalbertspijkers.blogspot.de/2014/03/cloudstack-versus-openstack-versus.html.














\end{thebibliography}



http://www.rackspace.com/blog/how-the-open-cloud-powers-academic-and-scientific-research/
https://www.ci.uchicago.edu/research-centers/open-science-data-cloud
https://rc.fas.harvard.edu/news-home/feature-stories/research-computing-partner-in-massachusetts-open-cloud-project/
http://www.bu.edu/hic/projects/massachusetts-open-cloud/
http://www.cs.bu.edu/fac/best/res/papers/ic14.pdf
http://nectar.org.au/

http://www.rackspace.com/blog/how-the-open-cloud-powers-academic-and-scientific-research/
https://www.ci.uchicago.edu/research-centers/open-science-data-cloud
https://rc.fas.harvard.edu/news-home/feature-stories/research-computing-partner-in-massachusetts-open-cloud-project/
https://www.opensciencedatacloud.org/projects/
https://www.opensciencedatacloud.org/publicdata/
http://www.bu.edu/hic/projects/massachusetts-open-cloud/
http://www.cs.bu.edu/fac/best/res/papers/ic14.pdf
http://nectar.org.au/
