\begin{abstract}


The report summarizes my work in the past semester in the IT security team of the chair "Internet Technologies and Systems". The report contains my views about research work and reflects certain activities in research projects.

The testbed is an important part of any research work in the area of network security and security analytics. Common testbeds are data and test network environments. The absence and the need to create new testbed make an overhead of research work and, as a result, this overhead slows down research progress. Therefore, the issue of automation of testbed creation is crucial goal to accelerate research progress. In this report we show methods, ideas and ways which we use for solving problems of the lack of data and the absent of test network environments. They are presented in the second and the third sections of the report. The second section of the report reflects a method of solving the issue of the lack of data for the certain research project in the security analytics area.
The third section of the report reflects the issue of the absence of test network environments and ways of solving the problem. This section includes an overview of the Security Lab Generator project, an overview of the OpenStack project and ideas how they can be used for solving the problem.

The goal of the report is to show methods and identify research challenges in solving the problem of testbed automation for network security and security analytics and suggest the ways of solving them.


\end{abstract}